Survival Analysis

### 2014-03-31 presentation.Rnw
Figured out hazards function
It's an odds ratio, not a probability. Internets are so fucking wrong.

\begin{frame}{Descriptors}
Assume $f(t)$ is the instantaneous failure rate

@@

% Hazard stuff is wrong
\begin{tabular}{lllcc}
Survival
  & $P(\mbox{no event in } t_i < t)$
  & $S(t)$ & = & $\int^{t}_{0} f(x)$ \\
Hazard
  & $P(\mbox{no event until } t)$
  & $\lambda(t)$ & = & $^{f(t)} / _{S(t)}$ \\
Cum. \\ Hazard
  & E()
  & $\Lambda(t)$ & = & $\int^{t}_{0} \lambda(t) dt$ \\
\end{tabular}
\end{frame}

\begin{frame}{Descriptors}
\begin{tabular}{lcc}
  & independent & conditional \\
  instantaneous & $f(t)$ & $\lambda(t)$ \\
  cumulative & $S(t)$ & $\Lambda(t)$
\end{tabular}
\end{frame}

>>>>

\begin{frame}{Descriptors}
Assume $f(t)$ is the instantaneous probability of the event occurring.

@@

\begin{tabular}{lllcc}
Survival
  & $P(\mbox{no event before } t)$
  & $S(t)$ & = & $1 - \int^{t}_{0} f(x)$ \\
Hazard
  & $OR(\mbox{no event until } t)$
  & $\lambda(t)$ & = & $^{f(t)} / _{S(t)}$ \\
Cumulative \\ Hazard
  & $OR(\mbox{event before } t)$
  & $\Lambda(t)$ & = & $\int^{t}_{0} \lambda(t) dt$ \\
\end{tabular}
\end{frame}

\begin{frame}{Descriptors}
\begin{tabular}{lcc}
  & probability & odds ratio \\
  instantaneous & $f(t)$ & $\lambda(t)$ \\
  cumulative & $S(t)$ & $\Lambda(t)$
\end{tabular}
\end{frame}
